---
title: "DATA501 Assignement 1 - Corvin Idler - ID 300598312"
output:
  pdf_document: default
  html_document: default
date: "2024-07-23"
---

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)

```
The link to to the code respositry underpinning this file is: https://github.com/econdatatech/DATA501-A1

# Code of the Shapiro-Wilk test function
This section will download the main.R file from the repository (to make sure code is maintained at one single place)
So it needs a working internet connection.
The additional parameter (Interpret=TRUE) of my function allows to output the result in textform in a whole sentence.
The implementation is based on https://www.tandfonline.com/doi/abs/10.1080/02664769723828

```{r}
download.file('https://raw.githubusercontent.com/econdatatech/DATA501-A1/main/main.R','main_.R',quiet=T)
knitr::spin_child('main_.R')
```

```{r}
shapirowilk(c(2,Inf,3,NA,2,4,4))

shapirowilk(c(2,3,2,4,4),T)
```



# Test cases for the Shapiro-Wilk test function
We use the testthat package to perform unit tests for presence of NA, Inf values, as well as wrong data type.
We also test the case of running the function with valid input data.
I decided to autofix presence of NA and Inf in the function. So the presence of these values will throw warnings not errors. 
The test cases account for that.
```{r}
library(testthat)

# Test for NA warnings
test_that("we test NA handling of shapirowilk()", {
    expect_warning(shapirowilk(c(2, 3, NA, 2, 4, 4)),
                   
    'It appears that the input vector contains NA values. 
                     They will be filterd out.')
})

# Test for Inf warnings
test_that("we test Inf handling of shapirowilk()", {
    expect_warning(shapirowilk(c(2, 3, Inf, 2, 4, 4)),
                   
    'It appears that the input vector contains INF values. 
                     They will be filterd out.')
})

# Test for wrong data types
test_that("we test wrong data type handling of shapirowilk()", {
    expect_error(shapirowilk(c(2, 3, 'a', 2, 4, 4)),
    'is.numeric\\(x\\) is not TRUE')
})

# Test with correct input data
test_that("We test shapirowilk() with correct input", {
    expect_no_error(shapirowilk(rnorm(1000)))
})


```